% !TEX root = slides.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[t]
\label{lit}
\frametitle{Literature \hfill \hspace*{7cm}}

\vspace*{-0.3cm}

\begin{tiny}
{\parindent=0pt


 \scriptsize{\underline{General PC}}\tiny

% \medskip
%  N. Wiener, ``Homogeneous Chaos", \emph{American Journal of Mathematics}, 60(4), 897-936, (1938).

\medskip
 Ghanem, R., Spanos, P., ``Stochastic Finite Elements: A Spectral Approach",
Springer Verlag, (1991).

\medskip
 Xiu, D., Karniadakis, G., ``The Wiener-Askey Polynomial Chaos for Stocahstic Differential
Equations", \textit{SIAM J. Sci. Comp.}, 24(2), 619-644, (2002).

\medskip
 Le Ma{\^\i}tre, O., Knio, O., ``Spectral Methods for Uncertainty Quantification:
With Applications to Computational Fluid Dynamics", Springer-Verlag, (2010).

\medskip
 Najm, H., ``Uncertainty Quantification and Polynomial Chaos Techniques in Computational
Fluid Dynamics", \textit{Ann. Rev. Fluid Mech.}, 41(1):35-52, (2009).


\medskip
 Xiu, D., ``Numerical Methods for Stochastic Computations: A Spectral Method
Approach", Princeton U. Press (2010).

%\bigskip
 %\scriptsize{\underline{Intrusive UQ}}\tiny

% \medskip
% Debusschere, B., Najm, H., P\'ebay, P., Knio, O., Ghanem, R., Le Ma{\^\i}tre, O.,
% ``Numerical Challenges in the Use of Polynomial Chaos Representations for Stochastic
% Processes", \textit{SIAM J. Sci. Comp.}, 26(2):698-719, (2004).

%\bigskip
% \scriptsize{\underline{PC surrogate}}\tiny

\medskip
 Marzouk, Y., Najm, H., ``Dimensionality Reduction and Polynomial Chaos Acceleration of
Bayesian Inference in Inverse Problems", \textit{J. Comp. Phys.}, 228(6):1862-1902, (2009).


\bigskip
 \scriptsize{\underline{Bayesian compressive sensing}}\tiny

\medskip
S. Ji, Y. Xue and L. Carin, ``Bayesian Compressive Sensing", \textit{IEEE Trans. Signal Proc.}, 56(6), (2008).

 \medskip
K. Sargsyan, C. Safta, H. Najm, B. Debusschere, D. Ricciuto, P. Thornton, ``Dimensionality reduction for complex models via Bayesian compressive sensing", \textit{Int. J. Uncertainty Quantification}, 4(1), 63-93, (2014).

\medskip
D. Ricciuto, K. Sargsyan, P. Thornton, ``The Impact of Parametric Uncertainties on Biogeochemistry in the E3SM Land Model", \textit{J of Advances in Modeling Earth Systems}, 10(2), 297-319, (2018).

\medskip
 \scriptsize{\underline{Model error}}\tiny


\medskip
M. Kennedy and A. O'Hagan, ``Bayesian calibration of computer models", \textit{Journal of the Royal Statistical Society}, Series B. 63, 425-464, (2001).

\medskip
K. Sargsyan, H. Najm, R. Ghanem, ``On the Statistical Calibration of Physical Models", \textit{Int. J. Chem. Kinetics}, 47(4), 246-276, (2015).

\medskip
K. Sargsyan, X. Huan, H. Najm. ``Embedded Model Error Representation for Bayesian Model Calibration", submitted to \emph{International Journal for Uncertainty Quantification}. ArXiv version, arXiv:1801.06768, (2018).

}

\end{tiny}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
